Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-08-09 paper/paper.tex
minor fixes

\begin{equation}
{\tt V = x.integrate;}
\end{equation}

@@

- compare with BRIAN, GENESIS, XPPAUT, NEURON, DynaSim \\
- selling point is ease of use and integration into MATLAB

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{Simulating a voltage-clamp experiment. (A) The diagram shows a cell with delayed rectifier potassium conductance (from \cite{liuModelNeuronActivitydependent1998}) that is being recorded from in two-electrode voltage clamp. (B) The code snippet shown here sets up a model with a single compartment and a single channel type, and clamps the cell to a constant voltage and integrates it. (C) Voltage steps that the cell is clamped to. (D) Current injected into the cell required to clamp it to the voltages in (C). (E) Asymptotic clamped current $vs.$ clamped voltage for this cell. (F) Accounting for the reversal potential of Potassium ions yields the conductance-voltage curve of this channel type. (G) Normalized conductance-voltage curves, with sigmoid fits with various exponents. (H) An exponent of $n=4$ yields the best fit, allowing for the characterization of the activation function of this channel type. }
	\label{fig:figureclamp}
\end{figure}

>>>>

\begin{lstlisting}[style=Matlab-editor]
	V = x.integrate;
\end{lstlisting}

@@

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_clamp}
	\caption{Simulating a voltage-clamp experiment. (A) The diagram shows a cell with delayed rectifier potassium conductance (from \cite{liuModelNeuronActivityDependent1998}) that is being recorded from in two-electrode voltage clamp. (B) The code snippet shown here sets up a model with a single compartment and a single channel type, and clamps the cell to a constant voltage and integrates it. (C) Voltage steps that the cell is clamped to. (D) Current injected into the cell required to clamp it to the voltages in (C). (E) Asymptotic clamped current $vs.$ clamped voltage for this cell. (F) Accounting for the reversal potential of Potassium ions yields the conductance-voltage curve of this channel type. (G) Normalized conductance-voltage curves, with sigmoid fits with various exponents. (H) An exponent of $n=4$ yields the best fit, allowing for the characterization of the activation function of this channel type. }
	\label{fig:figureclamp}
\end{figure}
